---
title: "Rworksheet_Holleza#3b.Rmd"
author: "Shun Holleza"
date: "2023-10-07"
output: pdf_document
---
  
```{r 1a}
household<-data.frame(Respondents <- 1:20, 
                      Sex <- c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
                      Fathers.Occupation <- c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1), 
                      Persons.at.Home <- c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
                      Siblngs.at.School <- c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
                      Types.of.Houses<- c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2))
household
```

```{r 1b}
str(household)
summary(household)
```

```{r 1c}
mean.sibling <- mean(household$Siblngs.at.School)
mean.sibling == 5
```

```{r 1d}
ss1<-household[1:2,]
ss1
```

```{r 1e}
ss2<- household[c(3,5), c(2,4)]
ss2
```

```{r 1f}
types_houses <- household$Types.of.Houses
types_houses
```

```{r 1g}
male.farmer <- subset(household, Sex == 1 & Fathers.Occupation == 1)
male.farmer
```

```{r 1h}
femalesiblings.respondents.greaterthan5<- subset (household, Sex == 2 & Siblngs.at.School == 5)
femalesiblings.respondents.greaterthan5
```

```{r 2a}
df = data.frame(Ints=integer(),
                Doubles=double(), Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
#2a. as the table show, the data frame has 0  observation and 5 variavbles. The factor column has nothiing to show since there are no values to define yet.

```{r 3}
household.data <- data.frame(respondents <- 1:10, 
                             sex<- c("Male", "Female", "Female", "Male", "Male", "Female", "Female",  "Male", "Female", "Male"), 
                             Fathers_Occupation <- c(1, 2, 3, 3, 1, 2, 2, 3, 1, 3),
                             Persons_at_Home<- c(5,7,3,8,6,4,4,2,11,6),
                             Sibling_at_School <- c(2,3,0,5,2,3,1,2,6,2),
                             Types_of_Houses<- c("Wood", "Congrete", "Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Congrete"))
household.data
write.csv(household.data, file = "HouseholdData.csv", row.names = FALSE)
household.data
```

```{r 3a}
household.data<-read.csv("HouseholdData.csv")
```

```{r 3b}
household.data$sex<- factor(household.data$sex)
household.data$sex<-as.integer(factor(household.data$sex,levels = c("Male", "Female"),labels = c(1,2)))
```

```{r 3c}
household.data$Types_of_Houses<- factor(household.data$Types_of_Houses)
household.data$Types_of_Houses<-as.integer(factor(household.data$Types_of_Houses, levels = c("Wood", "Congrete", "Semi-Congrete"), labels = c(1,2,3)))
print(household.data)
```

```{r 3d}
household.data$Fathers_Occupation<- factor(household.data$Fathers_Occupation)
household.data$Fathers_Occupation<-as.integer(factor(household.data$Fathers_Occupation, levels = c(1,2,3), labels = c("Farmer", "Driver", "Others")  ))
print(household.data)
```

```{r 3e}
female.drivers<- subset(household.data, sex==2 & Fathers_Occupation == "Driver" )
female.drivers
```

```{r 3f}
respondentsSiblingequalgreater5<- subset(household.data, Sibling_at_School >= 5)
respondentsSiblingequalgreater5
```

#4
The graph shows the sentiments or opinions that are labeled blue (Positive) red(negatvive) and yellow (neutral). It also has track of when were the sentiments recorded, also it has the level of sentiments  that are gathered with the mentioned dates from zero (0) to 4000. and below is my interpretation of data
July 14, 2020:
  - Negative: 2,500
- Neutral: 1,500 
- Positive: 1,750
July 15, 2020:
  - Negative:4,000 
- Neutral:2,750
- Positive:3,200
July 17, 2020:
  - Negative:3,250
- Neutral: 1,800 
- Positive: 2,500 
July 18, 2020:
  - Negative: 3,250 
- Neutral:  2,000 
- Positive: 2,500 

July 20, 2020:
  - Negative:  2,500 
- Neutral:  1,500
- Positive:  1,750 

July 21, 2020:
  - Negative :  4,000 
- Neutral : 2,600 
- Positive: 3,300 

base on the data, it seems like there are changes in the sentiments every month. which causes it to decrease and increase from time to time and is probably caused by a variety of factors.
